Title Goes Here

### 2020-01-30 paper/paper.tex
Paper progress

@@

In the example below, \texttt{example} would get transformed into \texttt{example'}:

@@

[Remove metadata from Generic representation and turn tree-like structure into a list-like structure]

\subsection{E, Rep, RepTy}

@@

\subsection{SumMatch}

\subsection{ProdMatch}

>>>>

\newcommand{\ttt}{\texttt}

@@

In the example below, \ttt{example} would get transformed into \ttt{example'}:

@@

\subsection{GHC Generics \ttt{Rep}}

[Remove metadata from Generic representation and turn tree-like structure into a (nested) list-like structure]

\subsection{\ttt{E}, \ttt{ERep}, \ttt{ERepTy}}

There are three interconnected foundational parts: \ttt{E}, \ttt{ERep} and
\ttt{ERepTy}. \ttt{E} is the deep embedding of the EDSL (a GADT that encodes
expressions in the DSL language). \ttt{ERep} is a type class which represents
all Haskell types which can be represented in the DSL. \ttt{ERepTy} is a type
family associated to the \ttt{ERep} type class, which represents a "canonical form"
of the given type. This canonical form can be immediately constructed in the EDSL.
Canonical form types crucially include \ttt{Either} and \ttt{(,)}, which
allow all combinations of basic sum types and product types to be encoded. More
information on this encoding is given in [a different section].

This information is brought into the \ttt{E} type via the constructor
\ttt{Repped}. The \ttt{E} also contains constructors representing \ttt{Either}
and \ttt{(,)} values:

\begin{lstlisting}
data E t where
  ...
  Repped :: ERep t => ERepTy t -> E t

  LeftExp :: E a -> E (Either a b)
  RightExp :: E b -> E (Either a b)

  PairExp :: E a -> E b -> E (a, b)
  ...
\end{lstlisting}

\ttt{ERep} and \ttt{ERepTy} provide an interface for transferring values between the EDSL
world and the Haskell world:

\begin{lstlisting}
class ERep t where
  type ERepTy t

  rep :: t -> E t
  rep = Repped . rep'

  unrep :: ERepTy t -> t

  rep' :: t -> ERepTy t
\end{lstlisting}

The key algebraic instances mentioned before are as follows:

\begin{lstlisting}
instance (ERep a, ERep b) => ERep (Either a b) where
  type ERepTy (Either a b) = Either a b

  rep (Left x) = LeftExp (rep x)
  rep (Right y) = RightExp (rep y)

  unrep = id
  rep'  = id

instance (ERep a, ERep b) => ERep (a, b) where
  type ERepTy (a, b) = (a, b)

  rep (x, y) = PairExp (rep x) (rep y)
  unrep = id
  rep'  = id
\end{lstlisting}

@@

Within the \ttt{E} expression language, a pattern match is represented by the
\ttt{CaseExp} constructor:

\begin{lstlisting}
data E t where
  ...
  CaseExp :: ERep t => E t -> SumMatch (ERepTy t) r -> E r
  ...
\end{lstlisting}

A value of type \ttt{SumMatch a b} represents a computation within the EDSL
which destructures a value of type \ttt{E a} and produces a value of type \ttt{E b}.
Therefore, \ttt{SumMatch (ERepTy t) r} represents a computation which destructures
a value of type \ttt{E (ERepTy t)} and produces a value of type \ttt{E b}.

\subsection{\ttt{SumMatch}}

The overall structure of \ttt{SumMatch} is a (heterogeneous) list of \ttt{ProdMatch} values.
Each item of this list corresponds exactly to one branch in the original \ttt{case} match.

\begin{lstlisting}
data SumMatch s t where
  SumMach ::
    (ERep a, ERep b, ERepTy b ~ b)
      => ProdMatch a r -> SumMatch b r -> SumMatch (Either a b) r

  EmptyMatch :: SumMatch Void r

  OneSumMatch ::
    (ERep a, ERep b, ERepTy a ~ a)
      => ProdMatch a b -> SumMatch a b
\end{lstlisting}

Note the \ttt{ERepTy a ~ a} constraints. This constraint ensures that the type \ttt{a}
is already in canonical form (that is, consists entirely of \ttt{Either}, \ttt{(,)} and
base types).

\subsection{\ttt{ProdMatch}}

\ttt{ProdMatch s t} is equivalent to a function a curried function from \ttt{s} to \ttt{t}.
Note that \ttt{s} will be a (potentially nested) pair type.
